Decentralisation of Poverty - Replication Analysis

### 2016-08-05 markdown/draft.RmD
do and tidy running and outputs of models

<!-- > round(apply(indicators_edinburgh, 2, quantile, c(0.5, 0.025, 0.975)),3) -->
<!--       RCI2004 RCI2012 D2004 D2012 -->
<!-- 50%     0.013  -0.013 0.385 0.319 -->
<!-- 2.5%    0.009  -0.016 0.382 0.316 -->
<!-- 97.5%   0.016  -0.009 0.389 0.322 -->
<!-- > ## Differences in RCI and D in 2011 - 2001 -->
<!-- > round(quantile(indicators_edinburgh[ ,2] - indicators_edinburgh[ ,1], c(0.5, 0.025, 0.975)),3) -->
<!--    50%   2.5%  97.5%  -->
<!-- -0.025 -0.030 -0.020  -->
<!-- > round(quantile(indicators_edinburgh[ ,4] - indicators_edinburgh[ ,3], c(0.5, 0.025, 0.975)),3) -->
<!--    50%   2.5%  97.5%  -->
<!-- -0.067 -0.071 -0.062  -->
<!-- >  -->
<!-- > indicators_aberdeen <- do_model("Aberdeen") -->
<!-- Keys match perfectly. -->

<!-- Keys match perfectly. -->

<!-- Joining by: "dz_2011" -->
<!-- data key contains NA's, which are ignored -->
<!-- Over coverage. 6628 out of 6975 unmatched data records: S01006789, S01006790, S01006791, S01006792, S01006793, ... -->
<!-- Setting up the model -->
<!-- Collecting 20000 samples -->
<!--   |====================================================================================| 100% -->
<!-- Summarising results -->
<!--  finished in  133.3 seconds -->
<!-- > round(apply(indicators_aberdeen, 2, quantile, c(0.5, 0.025, 0.975)),3) -->
<!--       RCI2004 RCI2012 D2004 D2012 -->
<!-- 50%     0.218   0.187 0.385 0.360 -->
<!-- 2.5%    0.213   0.181 0.379 0.355 -->
<!-- 97.5%   0.224   0.193 0.390 0.366 -->
<!-- > ## Differences in RCI and D in 2011 - 2001 -->
<!-- > round(quantile(indicators_aberdeen[ ,2] - indicators_aberdeen[ ,1], c(0.5, 0.025, 0.975)),3) -->
<!--    50%   2.5%  97.5%  -->
<!-- -0.031 -0.040 -0.022  -->
<!-- > round(quantile(indicators_aberdeen[ ,4] - indicators_aberdeen[ ,3], c(0.5, 0.025, 0.975)),3) -->
<!--    50%   2.5%  97.5%  -->
<!-- -0.024 -0.032 -0.017  -->

>>>>

### Change in RCI and D over time

```{r grab_posteriors, eval = TRUE, cache = FALSE, warning = FALSE, echo = FALSE}

all_posteriors <- read_csv("data/all_posterior_draws.csv") # Results from running the many models

all_posteriors  %>% 
  group_by(place, measure, period)  %>% 
  summarise(
    lower = quantile(value, 0.025), 
    median = quantile(value, 0.500), 
    upper = quantile(value, 0.975)
            ) -> posterior_summaries
```

Unlike the census-based variables used in Kavanagh, Lee & Pryce (2016), there are SIMD releases for 2004, 2006, 2009, 2012, and 2016, meaning in RCI and D scores within the period 2001 and 2011 can be observed. The Bayesian spatial modelling approach used by Kavanagh, Lee & Pryce (2016) was applied to each of the SIMD releases, and median RCI and D estimates, along with 95% CrIs, were produced for each release and for each city.

The graph of RCI over time is shown below.

```{r plot_change_rci, eval = TRUE, echo = FALSE, warning = FALSE}
# Do RCI graph
posterior_summaries %>% 
  filter(measure == "RCI") %>% 
   mutate(period = as.factor(period)) %>% 
   ggplot(., 
          aes(
            x = period, group = place, 
            y = median, colour = place,
            shape = place)) + 
   geom_line() + geom_point() + 
   scale_y_continuous(limits = c(0, 0.4) ) +
   geom_line(aes(y = upper), linetype = "dashed") + 
   geom_line(aes(y = lower), linetype = "dashed") + 
   labs(
     y = "RCI of income deprived", x = "Year", 
     title = "Change in RCI", 
     colour = "City", shape = "City") +
   theme(legend.position = c(0.8, 0.8))

This shows that the greatest falls in RCI occurred between the 2006 and 2009 SIMD releases

The plot of changes in D over time is shown below

```{r plot_change_d, eval = TRUE, echo = FALSE, warning = FALSE}
# Do D graph

posterior_summaries %>% 
  filter(measure == "D") %>% 
  mutate(period = as.factor(period)) %>% 
  ggplot(., 
         aes(
           x = period, group = place, 
           y = median, colour = place,
           shape = place)) + 
  geom_line() + geom_point() + 
  scale_y_continuous(limits = c(0, 0.5) ) +
  geom_line(aes(y = upper), linetype = "dashed") + 
  geom_line(aes(y = lower), linetype = "dashed") + 
  labs(
    y = "D of income deprived", x = "Year", 
    title = "Change in D", 
    colour = "City", shape = "City") +
  theme(legend.position = c(0.8, 0.8))

Similarly, the the greatest fall in D occurred between 2006 and 2009.
